---
output: html_document
editor_options: 
  chunk_output_type: console
---

Setting up the required working directory

```{r}
setwd("D:/Retails")
```


#reading the test and train data from CSV files
```{r}
retail_train <- read.csv("store_train.csv", stringsAsFactors = F)
retail_test  <- read.csv("store_test.csv", stringsAsFactors = F)

#combining data for wrangling purposes

names(retail_train)
names(retail_test)
retail_test$store <- NA
retail_train$data <- "train"
retail_test$data <- "test"

retail_all <- rbind(retail_train, retail_test)
```


#Data Cleaning Required
```{r}

#checking for NA Values in our data

s <- sapply(retail_all, function(x) sum(is.na(x)))
s <- which(s > 0)

#Let's fill NA values in country with missing data and population with mean values

retail_all$country[is.na(retail_all$country)] <- "Missing_Value"
retail_all$population[is.na(retail_all$population)] <- mean(retail_all$population, na.rm = T)

library(dplyr)
glimpse(retail_all)

```


Creating Dummies for character variables
```{r}
CreateDummies=function(data,var,freq_cutoff=100){ 
  t=table(data[,var]) 
  t=t[t>freq_cutoff] 
  t=sort(t)
  categories=names(t)[-1]
for( cat in categories){ name=paste(var,cat,sep="_")
name=gsub(" ","",name)
name=gsub("-","_",name) 
name=gsub("\\?","Q",name) 
name=gsub("<","LT_",name) 
name=gsub("\\+","",name) 
name=gsub(">","GT_",name)
name=gsub("=","EQ_",name) 
name=gsub(",","",name) 
name=gsub("/","_",name) 
data[,name]=as.numeric(data[,var]==cat)
  }
data[,var]=NULL 
return(data)
}

#here country and state variable is numeric which should have character

retail_all$country <- as.character(retail_all$country)
#retail_all$State <- as.character(retail_all$State)

#similary cousub and countyname are to be character data types

retail_all$CouSub <- as.character(retail_all$CouSub)
retail_all$countyname <- as.character(retail_all$countyname)

sort(table(retail_all$country), decreasing = T)

sapply(retail_all, function(x) length(unique(x)))

#store code should not be considered as it is corresponds to areaname.. 

retail_all <- select(retail_all, -c(storecode, State))

#checking for values with characters nd unique values

char_logical=sapply(retail_all,is.character)
cat_cols=names(retail_all)[char_logical] 
cat_cols
#data doesn't require dummy variable
cat_cols = cat_cols[!(cat_cols %in% c('data'))]
names(retail_all)
sapply(retail_all, function(x) class(x))
for(col in cat_cols) {
  retail_all <- CreateDummies(retail_all, col, 100)
}

#creating total_sales column
retail_all$total_sales <- retail_all$sales0 + retail_all$sales1+retail_all$sales2+retail_all$sales3+retail_all$sales4

#now removing all sales except total_sales

retail_all <- select(retail_all, -c(sales0, sales1, sales2, sales3, sales4))
glimpse(retail_all)
```

#Filling for missing values now
```{r}
missing <- sapply(retail_all, function(x) sum(is.na(x)))
which(missing > 0)

unique(retail_all$country_21)
```

#separate test and train data
```{r}
retail_train <- retail_all %>% filter(data == "train") %>% select(-c(data))
retail_test <- retail_all %>%  filter(data == "test") %>%  select(-c(data, store))
```


#Split train into two for testing purposes
```{r}
set.seed(2)
s= sample(1:nrow(retail_train), 0.75*nrow(retail_train))
retail_train1 <- retail_train[s,]
retail_train2 <- retail_train[-s,]

#let's build our model on train1, checking for VIF using linear regression firstly

for_vif <- lm(store~.-Id, data=retail_train1)
library(car)
sort(vif(for_vif), decreasing = T)[1:3]
#removing sales0 variable
for_vif <- lm(store~.-Id, data=retail_train1)
#we could note that sales variable are related to each another, it's better to find sum
sort(vif(for_vif), decreasing = T)[1:3]
#values are good enough now to proceed
alias(for_vif)
#with above I could note that state_alpha variable is related to state variable, hence
#repeating the process by removing state variable
summary(for_vif)

log_fit <- glm(store~.,data = retail_train1, family = "binomial")
summary(log_fit)
```


#Predicting on our test data
```{r}

library(pROC)
pred_val <- predict(log_fit, newdata = retail_train2, type = "response")

auc(roc(retail_train2$store,pred_val)) #-- 0.7713 good model
```

#Let's try using random forests

```{r}
param=list(mtry=c(5,10,15,20,26),
           ntree=c(50,100,200,500,700),
           maxnodes=c(5,10,15,20,30,50,100),
           nodesize=c(1,2,5,10)
           )


mycost_auc=function(y,yhat){
  roccurve=pROC::roc(y,yhat)
  score=pROC::auc(roccurve)
  return(score)
}


retail_train$store = as.factor(retail_train$store)
num_trials=25
my_params=subset_paras(param,num_trials)
my_params

myauc=0

library(cvTools)
library(randomForest)
## Cvtuning
## This code will take couple hours to finish
## Dont execute in the class
for(i in 1:num_trials){
  print(paste('starting iteration :',i))
  # uncomment the line above to keep track of progress
  params=my_params[i,]
names(retail_train)  
  names(retail_train)
  k=cvTuning(randomForest,store~.-Id, 
             data =retail_train,
             tuning =params,
             folds = cvFolds(nrow(retail_train), K=10, type ="random"),
             cost =mycost_auc, seed =2,
             predictArgs = list(type="prob")
             )
  score.this=k$cv[,2]
  
  if(score.this>myauc){
    print(params)
    # uncomment the line above to keep track of progress
    myauc=score.this
    print(myauc)
    # uncomment the line above to keep track of progress
    best_params=params
  }
  
  print('DONE')
  # uncomment the line above to keep track of progress
}

```



#Predicting probs(scores) on model for test data
```{r}
hr.rf.final=randomForest(store~.,
                         mtry=best_params$mtry,
                         ntree=best_params$ntree,
                         maxnodes=best_params$maxnodes,
                         nodesize=best_params$nodesize,
                         data=retail_train
                         )

test.score=predict(hr.rf.final,newdata = retail_test,type='prob')[,2]
store <- data.frame(test.score)
write.csv(test.score,'Manoj_Garikapati_P2_part2.csv',row.names = F)
```

```









